Treatment Outcome Visualization

### 2023-09-20 Treatment_Outcomes.Rmd
POST SCORES!

#2. Create pre_scores
      CUXOS_pre = Day1_CUXOS,
      CUDOS_pre = Day1_CUDOS
      ) %>%

@@

#5. Then create df with CUDOS and CUXOS scores
  # Depression

    CUDOS_Score <- select(Mothership_post,
                      Day1_CUDOS:Day40_CUDOS)
    CUDOS_Score <- data.frame(CUDOS_Score)

  # Anxiety
    CUXOS_Score <- select(Mothership_post, Day1_CUXOS:Day40_CUXOS)
    CUXOS_Score <- data.frame(CUXOS_Score)

@@

#9. Convert to data frame with means of values to be plotted
AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
  group_by(Test,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

>>>>

#2. Create pre_scores
      CUXOS_pre = Day1_CUXOS,
      CUDOS_pre = Day1_CUDOS,
      dummy = -99
      ) %>%

@@

#5. Then create df with CUDOS and CUXOS scores
  # Depression
Mothership_post
    CUDOS_Score <-    
                      select(Mothership_post,
                      Day1_CUDOS:Day40_CUDOS)
    CUDOS_Score <- data.frame(CUDOS_Score)

  # Anxiety
    CUDOS_Score <- select(Mothership_post, dummy,Day1_CUXOS:Day40_CUXOS)
    CUXOS_Score <- data.frame(CUXOS_Score)

@@

#9. Convert to data frame with means of values to be plotted
AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
  group_by(Test,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))
```

```{r}
#load DF
nrow(CUDOS_Score)
CUDOS_Score

CUDOS_Score_Test <- CUDOS_Score[1:20,]
CUDOS_Score_Test

new_var <- NA
data <- NA
# new_var <- data.frame(new_var)
for(i in 1:nrow(CUDOS_Score)){
data <- unname(unlist(CUDOS_Score[i,]))
data <- data[!is.na(data)]
data <- tail(data, n=1)
new_var <- rbind(new_var,data)
}

new_var

first_var <-rbind(first_var,first)
last_var

pre_post <-data.frame(first_var,last_var)

pre_post

new_var
nrow(new_var)

Mothership_post <- mutate(Mothership_post,

                          )

# Mothership_post$Days_complete_W
